Data Cleaning

### 2024-02-21 modeling_data/GLOBI_bee_update_clean.Rmd
adding script that got deleted

## Remove plants not id'd to at least genus level, and bees that are not id'd to species
## Change old family names for Asteraceae, Lamiaceae and Apiaceae
```{r}
#reformat the interactions data:
interactions_reformat = interactions_b %>% 
  mutate(scientificName = capitalize(sourceTaxonSpeciesName), 
         bee_family = capitalize(sourceTaxonFamilyName),
         plant_family = capitalize(targetTaxonFamilyName), 
         plant_genus = capitalize(targetTaxonGenusName),
         plant_species = capitalize(targetTaxonName)) %>%
  filter(scientificName != '' & plant_family !='' & plant_genus != "") %>%
  filter(targetTaxonRank %in% c('subspecies','species',"genus",'subgenus','variety')) %>%
  filter(sourceTaxonRank %in% c("subspecies",'variety','species')) %>%
  mutate(plant_family = ifelse(plant_family=='Compositae','Asteraceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Umbelliferae','Apiaceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Labiatae','Lamiaceae',plant_family)) 
```

>>>>

## Remove plants not id'd to at least genus level, and bees that are not id'd to species
## Change old family names for Asteraceae, Lamiaceae and Apiaceae
```{r}
#some of these are not vascular plants or not id'd to genus (e.g Heliantheae)
rm_me = c("Coleoptera","White","Picconiella","Heliantheae","Eupatorieae","Eremocarpus") #Eremocarpus is now split into 3 different genera

#reformat the interactions data:
interactions_reformat = interactions_b %>% 
  mutate(scientificName = capitalize(sourceTaxonSpeciesName), 
         bee_family = capitalize(sourceTaxonFamilyName),
         plant_family = capitalize(targetTaxonFamilyName), 
         plant_genus = capitalize(targetTaxonGenusName),
         plant_species = capitalize(targetTaxonName)) %>%
  filter(scientificName != '' & plant_family !='' & plant_genus != "") %>%
  filter(targetTaxonRank %in% c('subspecies','species',"genus",'subgenus','variety')) %>%
  filter(sourceTaxonRank %in% c("subspecies",'variety','species')) %>%
  mutate(plant_family = ifelse(plant_family=='Compositae','Asteraceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Umbelliferae','Apiaceae',plant_family)) %>%
  mutate(plant_family = ifelse(plant_family=='Labiatae','Lamiaceae',plant_family)) %>% filter(!plant_species %in% rm_me)
